Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-11 draft/accordionComplexSurfaces.tex
Minor changes

\begin{proposition}
\label{prop:flip}
Let~$F$ be a non-kissing facet in~$\NKC$ and let~$\omega \in F$ be a bending walk.
Let~$\alpha$ and~$\beta$ be the distinguished arrows of~$\omega$ (see Proposition \ref{prop:numberOfDistinguishedArrows}), and~$\sigma$ be the distinguished substring of~$\omega$, which splits~$\omega$ into~$\omega = \rho \sigma \tau$.
Let~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~$\alpha'\alpha \in I$ or~$\alpha\alpha' \in I$, and $\beta'\beta \in I$ or~$\beta\beta' \in I$.
Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$ be the distinguished walks of~$F \ssm \{\omega\}$ at~$\alpha'$ and~$\beta'$ respectively.
Then
\begin{enumerate}[(i)]
\item The walk~$\mu$ splits into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ splits into~$\nu = \rho \sigma \tau'$.
\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$. Moreover, $\omega'$ is the only other (undirected) walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
\end{enumerate}
\end{proposition}
The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} of \defn{mutation} of~$F$ at~$\omega$.
The flip is \defn{positive} if~$\sigma$ is on top of~$\omega$, and \defn{negative} otherwise.

@@

\vincent{Add a description and a schematic representation of the flip in the accordion complex and in the slalom complex.}

>>>>

\begin{proposition}
\label{prop:flip}
Let~$F$ be a non-kissing facet in~$\NKC$ and let~$\omega \in F$ be a bending walk.
Let~$\alpha$ and~$\beta$ be the distinguished arrows of~$\omega$ (see Proposition \ref{prop:numberOfDistinguishedArrows}), and~$\sigma$ be the distinguished substring of~$\omega$, which splits~$\omega$ into~$\omega = \rho \sigma \tau$.
Let~$\alpha'$ and~$\beta'$ be the other two arrows of~$Q_1\blossom$ incident to the endpoints of~$\sigma$ and such that~$\alpha'\alpha \in I$ or~$\alpha\alpha' \in I$, and $\beta'\beta \in I$ or~$\beta\beta' \in I$.
Let~$\mu \eqdef \distinguishedWalk{\alpha'}{F \ssm \{\omega\}}$ and~$\nu \eqdef \distinguishedWalk{\beta'}{F \ssm \{\omega\}}$ be the distinguished walks of~$F \ssm \{\omega\}$ at~$\alpha'$ and~$\beta'$ respectively.
Then
\begin{enumerate}[(i)]
\item The walk~$\mu$ splits into~$\mu = \rho' \sigma \tau$ and the walk~$\nu$ splits into~$\nu = \rho \sigma \tau'$.
\item The walk~$\omega' \eqdef \rho' \sigma \tau'$ is kissing~$\omega$ but no other~walk~of~$F$. Moreover, $\omega'$ is the only other (undirected) walk besides~$\omega$ which is not kissing any other walk of~$F \ssm \{\omega\}$.
\end{enumerate}
\end{proposition}
The walk~$\omega'$ of Proposition \ref{prop:flip} is the \defn{flip} or \defn{mutation} of~$F$ at~$\omega$.
The flip is \defn{positive} if~$\sigma$ is on top of~$\omega$, and \defn{negative} otherwise.

@@
